---
title: "Aggregates_in_R"
author: "Ashwini Nayak"
date: "20/01/2020"
output: pdf_document
---

```{r message = FALSE}
# load packages
library(readr)
library(dplyr)
```

```{r message = FALSE}
# load data
orders <- read_csv("orders.csv")
page_visits <- read_csv("page_visits.csv")
```

```{r}
# inspect data frames
head(orders)
head(page_visits)
```

```{r}
# average price of order
average_price <- orders %>% 
  summarize(mean_price = mean(price, na.rm = TRUE))
average_price
```

```{r}
# page visits by UTM source
click_source <- page_visits %>%
  group_by(utm_source) %>%
  summarize(count = n())
click_source
```

```{r}
# page visits by UTM source and month
click_source_by_month <- page_visits %>%
  group_by(utm_source,month) %>%
  summarize(count = n())
click_source_by_month
```

# inspect orders here:
head(orders,10)
```

```{r}
# define most_expensive here:
most_expensive <- orders %>% 
summarize(max_price = max(price,na.rm = TRUE))

most_expensive
```

```{r}
# define num_colors here:
num_colors <- orders %>%
    summarize(n_colors = n_distinct(shoe_color))

num_colors
```

```{r}
# define pricey_shoes here:
pricey_shoes <- orders %>%
      group_by(shoe_type) %>%
      summarize(max_price = max(price, na.rm =TRUE))

pricey_shoes
```

```{r}
# define shoes_sold here:
shoes_sold <- orders %>%
        group_by(shoe_type) %>%
        summarize(total = n())

```

```{r}
# define shoe_counts here:
shoe_counts <- orders %>%
        group_by(shoe_type, shoe_color) %>%
        summarize(count = n())
```

```{r}
# define shoe_prices here:
shoe_prices <- orders %>%
      group_by(shoe_type, shoe_material) %>%
      summarize(avg = mean(price, na.rm = TRUE))
```

```{r}
# define most_pop_orders here:
most_pop_orders <- orders %>%
      group_by(shoe_type) %>%
      filter(n() > 16)

most_pop_orders
```

```{r}
# define diff_from_mean here:
 diff_from_mean <- orders %>% 
        group_by(shoe_type) %>%
        mutate( diff_from_shoe_type_mean = price - mean(price,na.rm = TRUE))
```

```{r}
# define average_price here:

average_price <- orders %>%
      summarize(mean(price,na.rm = TRUE))
average_price
```

```{r}
# define click_source here:

click_source <- page_visits %>%
  group_by(utm_source) %>%
  summarize(clicks = n())

click_source   
```

```{r}
# define click_source_by_month here:
click_source_by_month <- page_visits %>%
      group_by(utm_source,month) %>%
      summarize(clicks_monthly = n())
```

